---
title: "Password cracking"
format: 
  html:
    toc: false
    css: css/styles.css
    echo: false
    mainfont: Helvetica, sans-serif
    embed-resources: true
---
```{r Notes}
#| include: false
# Print: render and print this document to save to PDF or directly print.
# Source: this problem is adapted from Project Euler, problem 79. https://projecteuler.net/problem=79
```

```{r LoadSettings}
#| include: false

knitr::opts_chunk$set(dev.args=list(bg="transparent"))
knitr::opts_chunk$set(dev.args = list(png = list(type = "cairo")))

# Load libraries
library(tidyverse)
library(grid)

# Load functions for docs
purrr::map(list.files(path = "./utils/", pattern = ".R$", recursive = TRUE, full.names = TRUE),
           source) %>%
  invisible()
```

``` {r SkillsRequiredBox}
#| output: asis
#| eval: true

# Output a box detailing the skills required for this challenge
## If you wish this to be a mystery, set eval to false
fSkillsRequired(c("Problem solving"))
```

``` {r DifficultyRating}
#| eval: true
#| fig-height: 0.7
#| fig-width: 4
#| fig-align: center

# Output a rating estimate to help the participants triage the activities
fDifficultyEstimate(0.4) %>%
  grid::grid.draw()
```

Someone installed a keylogger on my computer which incompletely captured every time I put the PIN in for this module. Thankfully it only randomly captured three characters each time in the order they appear in the PIN. If the passcode was 975318 and it captured the 2^nd^, 3^rd^, and 5^th^ characters, the keylogger output would be 751. Download the keylogger logfile. As a super genius I never put my passcode in wrong.

Given that the three characters are always asked for in order, determine the **shortest possible** passcode.